Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
paper

We also have the same decomposition of derived isomorphisms as in Lemma
\ref{lem:idcomppres}. We do not have to show functoriality of term substitution
here, since that is derivable in any CwF \cite{TODO}.

@@

First, we need to describe three model fragments of $\bM$, which can be
respectively used to compute notions of algebras, displayed algebras and
sections for each syntactic signature. This is a rephrasing of the
$\blank^{\A}$, $\blank^{\D}$ and $\blank^{\S}$ interpretations in
\cite{kaposi2019constructing}.

@@

We omit the rest of the definition of $\bT_{\ulOmega}$. The interpretations of equations in
the CwF and fl-structure parts become fairly technical, and we also need to
utilize iso-cleaving to interpret type substitution and substitution
laws. However, the basic shape of the model remains similar to
\cite{kaposi2019constructing}.
\end{definition}

>>>>

We also have the same decomposition of derived isomorphisms as in Lemma
\ref{lem:idcomppres}. We do not have to show functoriality of term substitution
here, since that is derivable in any CwF, see e.g. \cite{kaposi2019constructing}.

@@

We will need in the following three model fragments of $\bM$, which can be used
to compute notions of algebras, displayed algebras and sections respectively for
each syntactic signature. This is a rephrasing of the $\blank^{\A}$,
$\blank^{\D}$ and $\blank^{\S}$ interpretations in
\cite{kaposi2019constructing}.

@@

We omit the rest of the definition of $\bT_{\ulOmega}$. The interpretations of
equations in the CwF and the type formers are fairly technical, and we also
need to utilize iso-cleaving to interpret type substitution and substitution
laws. However, the basic shape of the model remains similar to
\cite{kaposi2019constructing}.
\end{definition}
